---
title: "My Training Activities"
format:
  html:
    toc: true
    page-layout: full
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(lubridate)
library(plotly)
library(leaflet)
library(DT)
library(tidygeocoder)
```

```{r}
# Load data
data.training <- read_csv("Data/CourseList.csv")

# Clean variable names
names(data.training) <- make.names(names(data.training))

# renaming
data.training <- data.training |>
  rename(Nb =  N.part, 
         Title = Topics)

# Dates
data.training$Start.date <- mdy(data.training$Start.date)
data.training$End.date   <- mdy(data.training$End.date)


# Other information
data.training <- data.training |>
  mutate(
    Format = case_when(Form =="B" ~ "F", 
                       Form == "W" ~"EL",
                       TRUE ~ Form), 
    Duration = as.numeric(End.date - Start.date) + 1, # +1 to count both start and end day
    Men = Nb - N.Female, 
    Women_perc = round(100*N.Female/Nb, 2)
  )

```

```{r}
Start_Period <-2020
```


```{r}
# FILTER: methodology trainings since the beginning of the period

methodology <- data.training |>
  filter(
    Category =="methodology"
  )
```

A selection of training activities delivered across the Asia-Pacific region
in data science, machine learning, and data visualization since my arrival at SIAP in 2020

---

## Face-to-Face Trainings 

*In-person workshops and training*

### Asia-Pacific Training Map

The map below shows locations where courses were delivered, with links from Chiba to each destination ;-).



```{r, cache=TRUE}
library(maps)
# GEOCODING
# Automatically obtain coordinates from locations

locations <- methodology |>
  filter(Year >= Start_Period)|>
  distinct(Location)

coords <- locations |>
  geocode(Location, method = "osm", lat = lat, long = lon) |>
  filter(!is.na(lat)) |>
  mutate(
    country = maps::map.where(x = lon, y = lat) |>  # returns "country:region"
      str_remove(":.*")                         # keep only country part
  )

methodology_map <- methodology |>
  left_join(coords, by = "Location") |>
  filter(!is.na(lat))
```


```{r}
# Tokyo / Chiba origin point
origin_lat <- 35.6074
origin_lon <- 140.1065
```


```{r}
# ── Destination summary (one row per unique location) ──────────────────────
dest_summary <- methodology_map |>
  filter(Location != "Chiba") |>
  group_by(country, Location, lat, lon) |>
  summarise(
    n_visits    = n(),
    is_duplicate = n() > 1,
    # Last visit = most recent year; break ties by Start.date if available
    last_title  = Title[which.max(Year)],
    last_year   = max(Year),
    last_nb     = Nb[which.max(Year)],
    .groups     = "drop"
  ) |>
  mutate(
    # Radius scales from 5 (1 visit) up, capped for readability
    marker_radius = 2 + (n_visits - 1) * 1,
    # Hover label
    hover_label = paste0( "<b>", country, ": ", "</b>",
       ifelse(n_visits == 1, "Single visit.", paste0( n_visits," visits.")), "<br>",
       ifelse(n_visits == 1, "", "Last visit:"), "<i> \"", last_title, "\" </i><br>",
      Location, " — ", last_year, "<br>",
      last_nb, " participants"
    )
  )
```


```{r}
# ── Base map ────────────────────────────────────────────────────────────────
m <- leaflet() |>
  addProviderTiles("CartoDB.Positron") |>
  # Origin point
  addCircleMarkers(
    lng        = origin_lon,
    lat        = origin_lat,
    radius     = 5,
    color      = "steelblue",
    fillColor  = "steelblue",
    fillOpacity = 1,
    popup      = "UNSIAP (Chiba)"
  )

```


```{r}
# ── Curved lines ─────────────────────────────────────────────────────────────
make_curve <- function(lon1, lat1, lon2, lat2, n = 100, curvature = 0.2) {
  t        <- seq(0, 1, length.out = n)
  mid_lon  <- (lon1 + lon2) / 2
  mid_lat  <- (lat1 + lat2) / 2
  dx       <- lon2 - lon1
  dy       <- lat2 - lat1
  curve_lon <- mid_lon - curvature * dy
  curve_lat <- mid_lat + curvature * dx
  lon <- (1 - t)^2 * lon1 + 2 * (1 - t) * t * curve_lon + t^2 * lon2
  lat <- (1 - t)^2 * lat1 + 2 * (1 - t) * t * curve_lat + t^2 * lat2
  tibble(lon, lat)
}

for (i in 1:nrow(dest_summary)) {
  dest  <- dest_summary[i, ]
  curve <- make_curve(
    origin_lon, origin_lat,
    dest$lon,   dest$lat,
    curvature  = 0.15
  )

  line_color   <- ifelse(dest$is_duplicate, "#e05c2a", "steelblue")
  line_weight  <- ifelse(dest$is_duplicate, 3, 1.2)
  line_opacity <- ifelse(dest$is_duplicate, 0.75, 0.5)

  m <- m |>
    addPolylines(
      lng     = curve$lon,
      lat     = curve$lat,
      color   = line_color,
      weight  = line_weight,
      opacity = line_opacity
    )
}
```



```{r}
# ── Destination markers (drawn AFTER lines so they sit on top) ──────────────
for (i in 1:nrow(dest_summary)) {
  dest <- dest_summary[i, ]

  m <- m |>
    addCircleMarkers(
      lng         = dest$lon,
      lat         = dest$lat,
      radius      = dest$marker_radius,        # ← scales with n_visits
      color       = ifelse(dest$is_duplicate, "#e05c2a", "navy"),
      fillColor   = ifelse(dest$is_duplicate, "#e05c2a", "navy"),
      fillOpacity = 0.75,
      # Click popup: full details of every visit if needed
      popup       = dest$hover_label,
      # Hover label
      label       = lapply(dest$hover_label, htmltools::HTML),
      labelOptions = labelOptions(
        style     = list(
          "font-weight" = "normal",
          "padding"     = "6px 10px",
          "line-height" = "1.6"
        ),
        textsize  = "11px",
        direction = "auto"
      )
    )
}

m
```

```{r}
Nb_Courses_F2F <- methodology%>%
  filter(Format == "F", 
         Location != "Chiba")%>%
  nrow()

Nb_Countries_F2F <- methodology%>%
  filter(Format == "F") %>%
  filter(!str_detect(Location ,"Chiba")) %>%
  distinct(Location,.keep_all = FALSE) %>%
  nrow()


```


In total, since `r Start_Period`,  I have conducted **`r Nb_Courses_F2F`** face-to-face courses in  **`r Nb_Countries_F2F`** countries (outside Japan). 

---

## E-Learning Trainings (EL)

Online and remote trainings in survey methodology and official statistics.

```{r}

el <- methodology |>
  filter(Format == "EL") |>
  arrange(desc(Start.date))
```

```{r}
el %>%
  select(
    Year,
    Start.date,
    Title,
    Nb,
    Women_perc
  ) %>%
datatable(
  rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(1, 'desc'))
  ),
 caption = paste0("E-learning courses (methodology category) - since ", Start_Period)
)
```

---

## Face to face

```{r}
F2F <- methodology |>
  filter(Format == "F") |>
  arrange(desc(Start.date))
```

```{r}
F2F %>%
  select(
    Year,
    Location, 
    Start.date,
    Title,
    Nb,
    Women_perc
  ) %>%
datatable(
  rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(2, 'desc'))  # sort according to Third column
  ),
  caption = paste0("Face-to-Face courses (methodology category) - since ", Start_Period)
)
```



# Over Time

```{r}
Courses_year <- data.training %>%
  filter(Year > 2015) %>%
  
  group_by(Year, Format) %>%
  summarise(
    n_courses      = n(),
    n_participants = sum(Nb, na.rm = TRUE),
    .groups        = "drop"
  ) |>
  arrange(desc(Year), Format)
  
```






```{r}
# Particpants
participants_year <- methodology |>
  group_by(Year) |>
  summarise(
    Women = sum(N.Female, na.rm = TRUE),
    Total = sum(Nb, na.rm = TRUE)
  ) |>
  mutate(
    Men = Total - Women
  )
```



```{r}
# Men and Women over time
participants_year |>
  pivot_longer(
    cols = c(Men, Women),
    names_to = "Gender",
    values_to = "Participants"
  ) |>

  ggplot(aes(x = Year,
             y = Participants,
             color = Gender)) +

  geom_line(linewidth = 1.2) +
  geom_point(size = 2.5) +

  scale_x_continuous(
    breaks = participants_year$Year
  ) +
  scale_color_manual(
    values = c(
      "Men" = "orange",
      "Women" = "purple"
    )
  ) +
  labs(
    title = "Participants per Year",
    x = NULL,
    y = "Participants",
    color = NULL
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "top",
    plot.title = element_text(face = "bold")
  )
```

