---
title: "My Training Activities"
format:
  html:
    toc: true
    page-layout: full
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(lubridate)
library(plotly)
library(leaflet)
library(DT)
library(tidygeocoder)
```

```{r}
# Load data
data.training <- read_csv("Data/CourseList.csv")

# Clean variable names
names(data.training) <- make.names(names(data.training))

# Dates
data.training$Start.date <- mdy(data.training$Start.date)
data.training$End.date   <- mdy(data.training$End.date)

# Men
data.training <- data.training |>
  rename(Nb =  N.part, 
         Title = Topics)|>
  mutate(
    Men = Nb - N.Female
  )

# FILTER: methodology trainings

methodology <- data.training |>
  filter(
    Category =="methodology"
  )
```

A selection of training activities delivered across the Asia-Pacific region
in data science, machine learning, and data visualization since my arrival at SIAP in 2020

---

## Face-to-Face Trainings (F)

In-person workshops and trainings

```{r}
f2f <- methodology |>
  filter(Form == "F" & Year >=2020) |>
  arrange(desc(Year),desc(Start.date))
```

```{r}
datatable(
  f2f |>
    select(
      Year,
      Start.date,
      Title,
      Location,
      Nb,
      N.Female
    ),
  rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(1, 'desc'))
  ),
  caption = "Face-to-face methodology trainings"
)
```

---

## E-Learning Trainings (EL)

Online and remote trainings in survey methodology and official statistics.

```{r}
el <- methodology |>
  filter(Form == "EL") |>
  arrange(desc(Start.date))
```

```{r}
datatable(
  el |>
    select(
      Year,
      Start.date,
      Title,
      Location,
      Nb,
      N.Female
    ),
  rownames = FALSE,
  options = list(
    pageLength = 15,
    order = list(list(1, 'desc'))
  ),
  caption = "E-learning methodology trainings"
)
```

---

# Participants Over Time

```{r}
participants_year <- methodology |>
  group_by(Year) |>
  summarise(
    Women = sum(N.Female, na.rm = TRUE),
    Total = sum(Nb, na.rm = TRUE)
  ) |>
  mutate(
    Men = Total - Women
  )
```



```{r}


participants_year |>
  pivot_longer(
    cols = c(Men, Women),
    names_to = "Gender",
    values_to = "Participants"
  ) |>

  ggplot(aes(x = Year,
             y = Participants,
             color = Gender)) +

  geom_line(linewidth = 1.2) +
  geom_point(size = 2.5) +

  scale_x_continuous(
    breaks = participants_year$Year
  ) +

  scale_color_manual(
    values = c(
      "Men" = "orange",
      "Women" = "purple"
    )
  ) +

  labs(
    title = "Participants per Year",
    x = NULL,
    y = "Participants",
    color = NULL
  ) +

  theme_minimal(base_size = 14) +

  theme(
    legend.position = "top",
    plot.title = element_text(face = "bold")
  )
```

---

# Asia-Pacific Training Map

The map below shows locations where methodology-related trainings were delivered,
with links from the UNSIAP area in Tokyo/Chiba to each destination.

```{r}
# GEOCODING
# Automatically obtain coordinates from locations

locations <- methodology |>
  filter(Year >= 2020)|>
  distinct(Location)

coords <- locations |>
  geocode(Location, method = "osm", lat = lat, long = lon)

methodology_map <- methodology |>
  left_join(coords, by = "Location") |>
  filter(!is.na(lat))
```

```{r}
# Tokyo / Chiba origin point
origin_lat <- 35.6074
origin_lon <- 140.1065
```

```{r}
m <- leaflet(methodology_map) |>

  addProviderTiles("CartoDB.Positron") |>

  # Origin point
  addCircleMarkers(
    lng = origin_lon,
    lat = origin_lat,
    radius = 8,
    color = "red",
    fillOpacity = 1,
    popup = "UNSIAP (Tokyo/Chiba)"
  ) |>

  # Training locations
  addCircleMarkers(
    lng = ~lon,
    lat = ~lat,
    radius = 5,
    color = "navy",
    popup = ~paste0(
      "<b>", Title, "</b><br>",
      Location, "<br>",
      Year, "<br>",
      Nb, " participants"
    )
  )
```

```{r}
# Add links from Tokyo/Chiba

for(i in 1:nrow(methodology_map)){

  m <- m |>
    addPolylines(
      lng = c(origin_lon, methodology_map$lon[i]),
      lat = c(origin_lat, methodology_map$lat[i]),
      weight = 1.2,
      opacity = 0.5
    )
}

m
```


```{r}
# Add curved links from Tokyo/Chiba
library(leaflet.extras2)

# Function to create curved line
make_curve <- function(lon1, lat1, lon2, lat2, n = 100, curvature = 0.2){

  t <- seq(0, 1, length.out = n)

  # Midpoint
  mid_lon <- (lon1 + lon2) / 2
  mid_lat <- (lat1 + lat2) / 2

  # Perpendicular offset for curvature
  dx <- lon2 - lon1
  dy <- lat2 - lat1

  curve_lon <- mid_lon - curvature * dy
  curve_lat <- mid_lat + curvature * dx

  # Quadratic Bezier curve
  lon <- (1 - t)^2 * lon1 +
         2 * (1 - t) * t * curve_lon +
         t^2 * lon2

  lat <- (1 - t)^2 * lat1 +
         2 * (1 - t) * t * curve_lat +
         t^2 * lat2

  tibble(lon, lat)
}

# Add curved lines
for(i in 1:nrow(methodology_map)) {

  curve <- make_curve(
    origin_lon,
    origin_lat,
    methodology_map$lon[i],
    methodology_map$lat[i],
    curvature = 0.15
  )

  m <- m |>
    addPolylines(
      lng = curve$lon,
      lat = curve$lat,
      color = "steelblue",
      weight = 1.2,
      opacity = 0.5
    )
}

m
```

